Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-09-06 paper.tex
edits to text and caption of Fig 7

We adopt a Kraichnan spectrum ($s=3/2$) for the fast modes, as seen in simulations \citep{cho03}. This can also be written as: 
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_L\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which
is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed
of waves. \C{Since the Kraichnan spectrum is critical in what follows, it is
  worthwhile taking a moment to recount the origin of the spectral slope $s$ and
  the cascade rate. In the magnetically dominated regime, two counterpropagating
  wave packets of scale $l$ interact on a wave crossing time $\tau_{\rm
    ph}=l/\varv_{\rm ph}$, rather than the eddy turnover time $\tau_{\rm edd} =
  l/\varv_{\rm l}$.  Since $\tau_{\rm ph} \ll \tau_{\rm edd}$, each interaction
  results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l}
  (\tau_{\rm ph}/\tau_{\rm edd})$. If these changes behave like a random walk,
  the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear
  ($\Delta \varv \sim \varv_{\rm l})$ and cascades to smaller scales occurs with
  a characteristic velocity $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm
    l}/\tau_{\rm ph})^{1/2} \sim \varv_{\rm l} (\tau_{\rm ph}/\tau_{\rm edd})\,
  (\tau_{\rm l}/\tau_{\rm ph})^{1/2}$, which we can solve to obtain the cascade
  time:
\begin{equation}
  \label{eqn:tau_l}
\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm ph}}\right)^{2} \tau_{\rm ph} \sim \frac{l \varv_{\rm ph}}{\varv_{\rm l}^{2}} 
\end{equation}
where we have implicitly assumed isotropy. This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm ph})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{\rm ph})^{1/4}$. Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum: 
\begin{equation}
E(k) \sim (\epsilon \varv_{\rm ph})^{1/2} k^{-3/2}.
\end{equation}}

@@

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\caption{Sensitivity of the radio emission in the Coma cluster to critical
  parameters. The left-hand panels show the radio surface brightness
  profiles. We compare profiles at 352~MHz \citep[blue
    crosses,][]{brown11} to predicted emission from Fermi-II
  reaccelerated CR electrons populations (black lines). The right-hand
  panels show radio synchrotron spectra. The green crosses are
  compiled from observations \citep{2010PhDT.......259P}, while the
  black lines show predicted spectra. The upper panels show the sensitivity to the level of
  turbulence ($X_\rmn{tu}$), the middle panels show the impact of
  different turbulent profiles ($\alpha_\rmn{tu}$), and the lower
  panels show the dependence on spatial distributions of initial and
  injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
  fiducial values for our model (solid lines), $X_\rmn{tu}=0.2$,
  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$ and vary each
  parameter separately in each row of panels. We find that the radio
  emission is most sensitive to the level of turbulence. The abundance of CR seeds, and the spatial distribution of CRs and turbulence play second-order effects.}
  \label{fig:param_comp}
\end{figure*}

@@

We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Figure
\ref{fig:param_comp}; note from equation (\ref{eq:Dpp_scaling}) that $\tau_{\rm D}
\propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
  tu}$ to explain the observations, it is worth understanding this property in
more detail. To this end, we ignore cooling, which is a good approximation for
the CR protons, because hadronic cooling times are long in comparison to the
other relevant timescales of the problem.\footnote{In principle, CRp can still
  lose energy via wave heating, at a rate $\left|\bmath{\varv_{\rm A} \cdot
    \nabla} P_\CR\right|$, but we assume CR streaming is suppressed during
  mergers, when they are spatially confined by scattering.} In this case,
$\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have $p
\rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the
fact that $\tau_{\rm D}$ is momentum independent). For an initial power law
distribution function $f(p) = C p^{-\alpha_{\rmn{inj}}}$, this momentum increase can be
rewritten as a change of normalisation, $f(p) = \tilde{C} p^{-\alpha_{\rmn{inj}}}$, where
$\tilde{C} = {\rm exp}( \alpha_{\rmn{inj}} \tau_{\rm cl}/\tau_{\rm D})$. A slightly more
careful derivation by direct solution of the Fokker-Planck equation yields:
\begin{equation}
  \dot{f} = {{\partial }\over{\partial p}}
  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
\end{equation}
with the analytic solution given by
\C{
\begin{equation}
  \label{eq:Creacc}
  \tilde{C}= 
  C \exp{\left[\frac{(2+\alpha_{\rmn{inj}})(\alpha_{\rmn{inj}}-1)}{4}\frac{t}{\tau_\rmn{D}}\right]}\,.
\end{equation}
At $t=\tau_\rmn{cl}$} the CR distribution is exponentially sensitive to
$\tau_{\rm cl}/\tau_{\rm D}$, which is the physical reason underlying
the extreme sensitivity to $X_{\rm tu}$ in
Figure~\ref{fig:param_comp}.

@@

\C{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolomogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}. The Burgers-like component does not reflect a genuine cascade, but rather the appearance of shocks which directly transfer power from large to small scales. At face value, we should use the Burgers spectrum for compressible modes. However, as already found by previous authors \citep{miniati15, brunetti16}, and as we shall discuss, this does not produce significant particle acceleration. If this is the correct spectrum, then the paradigm of turbulent particle acceleration is simply flawed, and some other mechanism is necessary to explain radio halos. Alternatively, it is well-known that due to mode-mode coupling,  solenoidal modes can give rise to compressive modes, and vice-versa \citep{kida90,cho03,kritsuk07}, even for subsonic turbulence, since pressure fluctuations of order $\sim \rho u^{2}$ arise. Indeed, note that many numerical studies (such as \citet{cho03,kritsuk07}) only have solenoidal driving on the outer scale, but then are also able to study the compressive modes that develop. In hydrodynamic turbulence, the energy in compressible modes which develop in this way scales as $\sim \mathcal{M}_{s}^2$, for $\mathcal{M}_{s} < 1$; this coupling is strongest at the Alfven scale \citep{cho03}. In MHD turbulence, mode-mode coupling is weak below the Alfven scale and the Alfven, fast and slow modes proceed as separate cascades.}

\C{We thus assume that some fraction of the Kolmogorov-like hydrodynamic turbulence which cascades down to the Alfven scale ends up as compressive fast modes with a Kraichnan spectrum, as seen in simulations \citep{cho03}. Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$. If some fraction $f_{\rm c}$ of the turbulent energy density at this scale is in compressible modes, then the energy density at the outer scale is $\sim f_{\rm c} \rho \varv_{\rm A}^{2}$.}
The turbulent reacceleration time is: 
\C{
  \begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{\beta}{f_{\rm c} \varv_{\rm A}^{2}}
\label{eqn:tau_D} 
\end{equation}
}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equations, \C{(\ref{eqn:diffusion}), (\ref{eqn:k_W}), (\ref{eqn:k_c}), assuming $s=3/2$}. The turbulent decay time is given by the cascade time of fast modes \C{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}): 
\begin{equation}
  \tau_{\rm decay} = \frac{\varv_{\rm ph}}{\varv_k^{2} k} = 
\frac{c_{\rm s}}{f_{\rm c} \varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation}
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm L}} \frac{c_{\rm s}^{2}}{f_{\rm c} \varv_{\rm L}^{2}}  \frac{\varv_{\rm A}}{c_{\rm s}} \approx  1.0 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{50} \right)^{-1/2}
\end{equation}
where we have used $\tilde{X}_{\rm tu} \approx f_{\rm c} (\varv_{\rm L}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. \C{The decay time at the Alfven scale is comparable (and could be larger, if $f_{\rm c}$ is smaller than we have assumed) to the eddy turnover time at the outer scale. Thus, it is appropriate to consider the latter as the decay time for the fast modes, rather than the cascade time at the driving scale. The reason for these comparable timescales despite the disparate lengthscales is that large scale hydrodynamic modes cascade on a single eddy turnover time, whereas small scale sub-Alfvenic MHD modes are in the weak turbulence limit, and require multiple wave-wave interactions for a mode to cascade.  }

@@

\sout{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}). We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.  They are remarkably revealing. In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population. This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}
\C{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values \footnote{When $\tau_{\rm D} \sim \tau_{\rm cl}$ is adopted, the radial behavior of $\tau_{\rm cl}$ is also changed. Since $\tau_{\rm D}$ decreases with radius (see e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease with the same amount which results in a steeper radio profile. To compensate for this in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR, spat}\rightarrow0.5$ and decrease the relative CR-to-thermal energy within the virial radius with a factor five to 0.06 per cent.} , but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm D} = 1/4 \,\tau_{\rm cl}$. They are remarkably revealing. In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.  This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}

For instance, in the top panels of Figure~\ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density does not matter -- profiles simply converge to an asymptotic form as $X_{\rm tu}$ is increased. This is in contrast to the exponential sensitivity, flattening in surface brightness, and increasing spectral curvature as $X_{\rm tu}$ is increased that we saw previously. A threshold value of $X_{\rm tu}$ is necessary for turbulent reacceleration to overcome cooling. Once that condition is satisfied, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ implies a fixed amount of amplification: stronger turbulence implies faster acceleration, but also dissipates more quickly. This leads to the asymptotic behaviour seen. From the middle panels, we see another striking result: in contrast to Figure~\ref{fig:param_comp}, results are also completely insensitive to the turbulent profile. Given the large uncertainties in the latter, this is a welcome property. It arises because for our fiducial value ($X_{\rm tu} = 0.2$), variations in the turbulent profile still lead to local energy densities which are above the threshold value required to overcome cooling, and turbulent amplification approaches its asymptotic value. Finally, in the bottom panels, we see that we {\it are} sensitive to the spatial profile of CRs; it affects both the radio surface brightness profile (a flatter CR distribution implies flatter surface brightness profiles) and luminosity (once again, luminosity is larger for more centrally concentrated CRs, since more secondaries are produced). This arises because once turbulent reacceleration overcomes cooling, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ provides for a fixed amount of amplification in each radial shell. The radio luminosity in each shell then depends linearly on initial conditions, i.e., the profile of CR seeds. Interestingly, the best-fitting profile for Coma comes from a flat CR distribution -- i.e., one that is the outcome of efficient CR streaming. Matching the overall amplitude simply involves a rescaling of $\tau_{\rm cl}/\tau_{\rm D}$ (equation \ref{eqn:ratios_CR_damp}) or the CR content.

Obviously, the ideas in this section require further study. However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty-- the poorly unconstrained properties of turbulence, and implies that radio haloes could potentially provide more robust constraints on the underlying CR population.

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{figure7_prof.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{figure7_spec.eps}
   \end{center}
\end{minipage}

>>>>

We adopt a Kraichnan spectrum ($s=3/2$) for the fast modes, as seen in simulations \citep{cho03}. This can also be written as: 
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_L\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which
is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed
of waves. \C{Since the Kraichnan spectrum is critical in what follows, it is
  worthwhile taking a moment to recount the origin of the spectral slope $s$ and
  the cascade rate. In the magnetically dominated regime, two counter-propagating
  wave packets of scale $l$ interact on a wave crossing time $\tau_{\rm
    ph}=l/\varv_{\rm ph}$, rather than the eddy turnover time $\tau_{\rm edd} =
  l/\varv_{\rm l}$.  Since $\tau_{\rm ph} \ll \tau_{\rm edd}$, each interaction
  results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l}
  (\tau_{\rm ph}/\tau_{\rm edd})$. If these changes behave like a random walk,
  the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear
  ($\Delta \varv \sim \varv_{\rm l})$ and cascades to smaller scales occurs with
  a characteristic velocity $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm
    l}/\tau_{\rm ph})^{1/2} \sim \varv_{\rm l} (\tau_{\rm ph}/\tau_{\rm edd})\,
  (\tau_{\rm l}/\tau_{\rm ph})^{1/2}$, which we can solve to obtain the cascade
  time:
\begin{equation}
  \label{eqn:tau_l}
\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm ph}}\right)^{2} \tau_{\rm ph} \sim \frac{l \varv_{\rm ph}}{\varv_{\rm l}^{2}} 
\end{equation}
where we have implicitly assumed isotropy. This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm ph})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{\rm ph})^{1/4}$. Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum: 
\begin{equation}
E(k) \sim (\epsilon \varv_{\rm ph})^{1/2} k^{-3/2}.
\end{equation}}

@@

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\caption{Sensitivity of the radio emission in the Coma cluster to
  critical parameters. The left-hand panels show the radio surface
  brightness profiles. We compare profiles at 352~MHz \citep[blue
    crosses,][]{brown11} to predicted emission from Fermi-II
  reaccelerated CR electrons (black lines). The right-hand panels show
  radio synchrotron spectra. The green crosses are compiled from
  observations \citep{2010PhDT.......259P}, while the black lines show
  predicted spectra. The upper panels show the sensitivity to the
  level of turbulence ($X_\rmn{tu}$), the middle panels show the
  impact of different turbulent profiles ($\alpha_\rmn{tu}$), and the
  lower panels show the dependence on spatial distributions of initial
  and injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
  fiducial values for our model (solid lines), $X_\rmn{tu}=0.2$,
  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$ and vary each
  parameter separately in each row of panels. We find that the radio
  emission is most sensitive to the level of turbulence. The abundance
  of CR seeds, and the spatial distribution of CRs and turbulence are
  second-order effects.}
  \label{fig:param_comp}
\end{figure*}

@@

We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Figure
\ref{fig:param_comp}; note from equation (\ref{eq:Dpp_scaling}) that $\tau_{\rm D}
\propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
  tu}$ to explain the observations, it is worth understanding this property in
more detail. To this end, we ignore cooling, which is a good approximation for
the CR protons, because hadronic cooling times are long in comparison to the
other relevant timescales of the problem.\footnote{In principle, CRp can still
  lose energy via wave heating, at a rate $\left|\bmath{\varv_{\rm A} \cdot
    \nabla} P_\CR\right|$, but we assume CR streaming is suppressed during
  mergers, when they are spatially confined by scattering.} In this case,
$\dot{p}= p/\tau_{\rm D}$, and after a time $\tau_{\rm cl}$, we have
\begin{equation}
  \label{eq:pexp}
p\rightarrow p \, {\rm exp}(\tau_{\rm cl}/\tau_{\rm D})
\end{equation}
(where we have used the fact that $\tau_{\rm D}$ is momentum independent). For
an initial power law distribution function $f(p) = C p^{-\alpha_{\rmn{inj}}}$,
this momentum increase can be rewritten as a change of normalisation, $f(p) =
\tilde{C} p^{-\alpha_{\rmn{inj}}}$, where $\tilde{C} = {\rm exp}(
\alpha_{\rmn{inj}} \tau_{\rm cl}/\tau_{\rm D})$. A slightly more careful
derivation by direct solution of the Fokker-Planck equation yields:
\begin{equation}
  \dot{f} = {{\partial }\over{\partial p}}
  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
\end{equation}
with the analytic solution given by
\C{
\begin{equation}
  \label{eq:Creacc}
  \tilde{C}= 
  C \exp{\left[\frac{(2+\alpha_{\rmn{inj}})(\alpha_{\rmn{inj}}-1)}{4}\frac{t}{\tau_\rmn{D}}\right]}\,.
\end{equation}
At $t=\tau_\rmn{cl}$} the CR distribution is exponentially sensitive to
$\tau_{\rm cl}/\tau_{\rm D}$, which is the physical reason underlying
the extreme sensitivity to $X_{\rm tu}$ in
Figure~\ref{fig:param_comp}.

@@

\C{In the hydrodynamic regime, a standard Hodge-Helmholtz decomposition usually shows that the compressive component of the velocity field is Burgers-like ($W(k) \propto k^{-2}$), while the solenoidal component is Kolmogorov-like ($W(k) \propto k^{-5/3}$), see e.g., \citet{federrath13}. The Burgers-like component does not reflect a genuine cascade, but rather the appearance of shocks which directly transfer power from large to small scales. At face value, we should use the Burgers spectrum for compressible modes. However, as already found by previous authors \citep{miniati15, brunetti16}, and as we shall discuss, this does not produce significant particle acceleration. If this is the correct spectrum, then the paradigm of turbulent particle acceleration is simply flawed, and some other mechanism is necessary to explain radio halos. Alternatively, it is well-known that due to mode-mode coupling,  solenoidal modes can give rise to compressive modes, and vice-versa \citep{kida90,cho03,kritsuk07}, even for subsonic turbulence, since pressure fluctuations of order $\sim \rho u^{2}$ arise. Indeed, note that many numerical studies (such as \citet{cho03,kritsuk07}) only have solenoidal driving on the outer scale, but then are also able to study the compressive modes that develop. In hydrodynamic turbulence, the energy in compressible modes which develop in this way scales as $\sim \mathcal{M}_{s}^2$, for $\mathcal{M}_{s} < 1$; this coupling is strongest at the Alfven scale \citep{cho03}. In MHD turbulence, mode-mode coupling is weak below the Alfven scale and the Alfven, fast and slow modes proceed as separate cascades.}

\C{We thus assume that some fraction of the Kolmogorov-like hydrodynamic turbulence which cascades down to the Alfven scale ends up as compressive fast modes with a Kraichnan spectrum, as seen in simulations \citep{cho03}. Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$. If some fraction $f_{\rm c}$ of the turbulent energy density at this scale is in compressible modes, then the energy density at the outer scale is $\sim f_{\rm c} \rho \varv_{\rm A}^{2}$.}
The turbulent reacceleration time is: 
\C{
  \begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{\beta}{f_{\rm c} \varv_{\rm A}^{2}}
\label{eqn:tau_D} 
\end{equation}
}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equations, \C{(\ref{eqn:diffusion}), (\ref{eqn:k_W}), (\ref{eqn:k_c}), assuming $s=3/2$}. The turbulent decay time is given by the cascade time of fast modes \C{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}): 
\begin{equation}
  \tau_{\rm decay} = \frac{\varv_{\rm ph}}{\varv_k^{2} k} = 
\frac{c_{\rm s}}{f_{\rm c} \varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation}
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm L}} \frac{c_{\rm s}^{2}}{f_{\rm c} \varv_{\rm L}^{2}}  \frac{\varv_{\rm A}}{c_{\rm s}} \approx  1.0 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{50} \right)^{-1/2}
\end{equation}
where we have used $\tilde{X}_{\rm tu} \approx f_{\rm c} (\varv_{\rm L}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. \C{The decay time at the Alfven scale is comparable (and could be larger, if $f_{\rm c}$ is smaller than we have assumed) to the eddy turnover time at the outer scale. Thus, it is appropriate to consider the latter as the decay time for the fast modes, rather than the cascade time at the driving scale. The reason for these comparable timescales despite the disparate length scales is that large scale hydrodynamic modes cascade on a single eddy turnover time, whereas small scale sub-Alfvenic MHD modes are in the weak turbulence limit, and require multiple wave-wave interactions for a mode to cascade.  }

@@

\sout{It is interesting to reconsider surface brightness and spectral profiles
  if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above
  (e.g., equation \ref{eqn:ratios_CR_damp}). We show the results of adopting
  such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
  Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm
    CR, spat}$ about fiducial values, but this time we do not adopt a fixed
  $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.  They are remarkably
  revealing. In this case, one is much less sensitive to the properties of the
  turbulence, and more sensitive to the details of the CR seed population. This
  gives hope to the possibility that one could effectively marginalise over the
  very uncertain properties of turbulence at larger scales in merging clusters
  (which are unlikely to be more precisely constrained observationally in the
  near future) to learn something about the underlying CR population.}  \C{It is
  interesting to reconsider surface brightness and spectral profiles if indeed
  $\tau_{\rm D} \sim \tau_{\rm cl}$ for the reasons mentioned above (e.g.,
  equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting such an
  ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to
  Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}$, $\alpha_{\rm tu}$, and
  $\alpha_{\rm CR, spat}$ about fiducial values.\footnote{\C{When $\tau_{\rm D}
      \sim \tau_{\rm cl}$ is adopted, the radial behaviour of $\tau_{\rm cl}$ is
      also modified. Because $\tau_{\rm D}$ decreases with radius (see
      e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease by the same
      amount, which results in a steeper radio profile. To compensate for this
      effect in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR,
        spat}=1.0\rightarrow0.5$ and decrease the relative CR-to-thermal energy
      within the virial radius by a factor five to $6\times10^{-4}$.}} Instead
  of adopting a fixed $\tau_{\rm cl}$, we set $\tau_{\rm D} = 1/4 \,\tau_{\rm
    cl}$. The results are remarkably revealing. In this case, we are indeed less
  sensitive to the properties of the turbulence, and more sensitive to the
  details of the CR seed population.  This gives hope to the possibility that
  one could effectively marginalise over the very uncertain properties of
  turbulence at larger scales in merging clusters (which are unlikely to be more
  precisely constrained observationally in the near future) to learn something
  about the underlying CR population.}

For instance, in the \C{third row of panels} of
Figure~\ref{fig:param_comp_tcl_tD}, we see that once turbulence exceeds a
threshold value $X_{\rm tu} \sim 0.1$, then its overall exact energy density
does not matter -- profiles simply converge to an asymptotic form as $X_{\rm
  tu}$ is increased. This is in contrast to the exponential sensitivity,
flattening in surface brightness, and increasing spectral curvature as $X_{\rm
  tu}$ is increased that we saw previously. A threshold value of $X_{\rm tu}$ is
necessary for turbulent reacceleration to overcome cooling. Once that condition
is satisfied, the condition $\tau_{\rm cl} \sim \tau_{\rm D}$ implies a fixed
amount of amplification: stronger turbulence implies faster acceleration, but
also dissipates more quickly. This leads to the asymptotic behaviour seen.

\C{The second row of panels of Figure~\ref{fig:param_comp_tcl_tD} reveal another
  striking result:} in contrast to Figure~\ref{fig:param_comp}, results are also
completely insensitive to the spatial profile of turbulence. Given the large
uncertainties, this is a welcome property. It arises because for our fiducial
value ($X_{\rm tu} = 0.2$), variations in the turbulent profile still lead to
local energy densities which are above the threshold value required to overcome
cooling, and turbulent amplification approaches its asymptotic value.

Finally, in the \C{top panels of Figure~\ref{fig:param_comp_tcl_tD}}, we see
that we {\it are} sensitive to the spatial profile of CRs; it affects both the
radio surface brightness profile (a flatter CR distribution implies flatter
surface brightness profiles) and luminosity (once again, luminosity is larger
for more centrally concentrated CRs, since more secondaries are produced). This
arises because once turbulent reacceleration overcomes cooling, the condition
$\tau_{\rm cl} \sim \tau_{\rm D}$ provides a fixed amount of amplification in
each radial shell. The radio luminosity in each shell then depends linearly on
initial conditions, i.e., the profile of CR seeds. Interestingly, the
best-fitting profile for Coma results from a flat CR distribution -- i.e., the
outcome of efficient CR streaming. Matching the overall amplitude simply
involves a rescaling of $\tau_{\rm cl}/\tau_{\rm D}$ (equation
\ref{eqn:ratios_CR_damp}) or the CR content.

Obviously, the ideas in this section require further study. However, the notion that $\tau_{\rm cl}/\tau_{\rm D}$ could self-regulate around a fixed value is exciting, because it eliminates the main source of uncertainty -- the poorly unconstrained properties of turbulence, and implies that radio haloes could potentially provide more robust constraints on the underlying CR population.
